Rapid-response Bayesian sky localization for electromagnetic follow-up of gravitational-wave candidates

### 2013-03-07 ms.tex
Meant \sim, not ~
Added more parameters

Ground-based \ac{GW} interferometers are entering the advanced detector era, positioning themselves to make profound discoveries about the universe. The advanced LIGO and Vigo detectors will be part of a worldwide network that also includes KAGRA and hopefully LIGO-India. Coalescing neutron star binaries are among the most likely sources, with event rates of $~ 50/\mathrm{yr}$ (check that number!)\cite{rates}. In addition to being an efficient source of \acp{GW}, the neutron star may be tidally shredded before merging, providing fuel for an electromagnetic counterpart. The short-lived accretion flow may power a collimated relativistic jet, resulting in a short gamma-ray burst and an X-ray afterglow if it is aligned with the line of sight. An optical afterglow may follow minutes to hours later as the jet plows into the interstellar medium. As surrounding neutron-rich ejecta decay radioactively, an optical `kilonova' may be visible after $~$1 day \cite{metzger:2010}. Finally, as the ejecta plow into the interstellar medium, a faint radio afterglow could occur on a timescale of weeks to years \cite{Nakar:2011cw}.

@@

A \ac{CBC} source is described by a 15\nobreakdashes-dimensional%
%
\marginpar{Check the number of parameters.}
%
parameter vector,
\begin{equation}
    \boldsymbol\theta = \begin{array}{l@{}l}
            \left[
            \begin{array}{c}
                \alpha \\
                \delta \\
                t_\oplus \\
                \iota \\
                \psi \\
                \phi_c \\
                \hdashline[1pt/1pt]
                m_1 \\
                m_2 \\
                \mathbf S_1 \\
                \mathbf S_2
            \end{array}
            \right] &
            \begin{array}{l}
                \left.
                \begin{array}{p{4cm}}
                    right ascension \\
                    declination \\
                    arrival time at geocenter \\
                    inclination angle \\
                    polarization angle \\
                    coalescence phase \\
                    \hdashline[1pt/1pt]
                \end{array}
                \quad \right\} \textnormal{extrinsic} \\
                \left.
                \begin{array}{p{4cm}}
                    first component's mass \\
                    second component's mass \\
                    first component's spin \\
                    second component's spin
                \end{array}
                \quad \right\} \textnormal{intrinsic}
            \end{array}
        \end{array}
\end{equation}

>>>>

Ground-based \ac{GW} interferometers are entering the advanced detector era, positioning themselves to make profound discoveries about the universe. The advanced LIGO and Vigo detectors will be part of a worldwide network that also includes KAGRA and hopefully LIGO-India. Coalescing neutron star binaries are among the most likely sources, with event rates of $~ 50/\mathrm{yr}$ (check that number!)\cite{rates}. In addition to being an efficient source of \acp{GW}, the neutron star may be tidally shredded before merging, providing fuel for an electromagnetic counterpart. The short-lived accretion flow may power a collimated relativistic jet, resulting in a short gamma-ray burst and an X-ray afterglow if it is aligned with the line of sight. An optical afterglow may follow minutes to hours later as the jet plows into the interstellar medium. As surrounding neutron-rich ejecta decay radioactively, an optical `kilonova' may be visible after $\sim$1 day \cite{metzger:2010}. Finally, as the ejecta plow into the interstellar medium, a faint radio afterglow could occur on a timescale of weeks to years \cite{Nakar:2011cw}.

@@

A \ac{CBC} source is specified by a vector of extrinsic parameters describing its position and orientation and intrinsic parameters describing the physical properties of the binary components:
%
\begin{equation}
    \boldsymbol\theta = \begin{array}{l@{}l}
            \left[
            \begin{array}{c}
                \alpha \\
                \delta \\
                D_\mathrm{L} \\
                t_\oplus \\
                \iota \\
                \psi \\
                \phi_c \\
                \hdashline[1pt/1pt]
                m_1 \\
                m_2 \\
                \mathbf S_1 \\
                \mathbf S_2
            \end{array}
            \right] &
            \begin{array}{l}
                \left.
                \begin{array}{p{4cm}}
                    right ascension \\
                    declination \\
                    luminosity distance \\
                    arrival time at geocenter \\
                    inclination angle \\
                    polarization angle \\
                    coalescence phase \\
                    \hdashline[1pt/1pt]
                \end{array}
                \quad \right\} \textnormal{extrinsic} \\
                \left.
                \begin{array}{p{4cm}}
                    first component's mass \\
                    second component's mass \\
                    first component's spin \\
                    second component's spin
                \end{array}
                \quad \right\} \textnormal{intrinsic}
            \end{array}
        \end{array}
\end{equation}
%
\marginpar{Citations needed. Do we want to mention these omitted parameters?}%
%
Binary eccentricity is omitted as an intrinisc parameter because \acp{GW} circularize the orbit long before the inspiral enters \ac{LIGO}'s frequency range of $\sim$10\nobreakdashes--1000~kHz. Tidal deformabilities of the components are omitted because tidal effects have a negligible effect in the inspiral phase.
